### 2021-07-06 src/figures/results/tables/student_infections_table.tex
New results uploaded without adjusting version.txt and no deleting previous results.

\begin{tabular}{lr}
\toprule
{} &  predicted total infections among 5-14 year olds from Easter until 2021-05-31 \\
scenario                               &                                                                               \\
\midrule
 educ open after easter  without tests &                                             725914 \\
 educ open after easter  with tests    &                                             552894 \\
 close educ after easter               &                                             430594 \\
 baseline                              &                                             439077 \\
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{lr}
\toprule
{} &  predicted total infections among 5-14 year olds from Easter until 2021-05-31 \\
scenario                               &                                                                               \\
\midrule
 educ open after easter  without tests &                                             696963 \\
 educ open after easter  with tests    &                                             545057 \\
 close educ after easter               &                                             422360 \\
 baseline                              &                                             432320 \\
\bottomrule
\end{tabular}
